Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-05-09 research_proposal/research_proposal_draft.qmd
Update research_proposal_draft.qmd
timeline and milestone

---
title: "Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators"
format: 
  pdf:
    include-in-header:
      text: |
        <!-- \usepackage{amsmath} -->
        <!-- \usepackage{mathspec} -->
        \usepackage{algorithm}
        \usepackage{algpseudocode}
        \usepackage[colorlinks=true, linkcolor=blue, citecolor=blue, urlcolor=blue]{hyperref}
    mathspec: true
    number-sections: true
execute:
  cache: true
bibliography: D:/Github/Recon_Honours_Thesis/references.bib
# bibliographystyle: apa
csl: D:/Github/Recon_Honours_Thesis/apa.csl
---

@@

- Put some graphs here

@@

```{r timeline}
#| echo: false
#| message: false
#| warning: false
library(tibble)
library(knitr)

tibble(
  Period = c(
    "March - April", 
    "May", 
    "June",
    "July", 
    "August - September",
    "October"
  ),
  Task = c(
    "Literature review, methods implementation (shrinkage, NOVELIST) + simulation framework",
    "Simulation + NOVELIST assessment",
    "Experiments with POET and PC-adjusted NOVELIST",
    "Exploration of other high-dimensional covariance estimators",
    "Real-world application + evaluation",
    "Final writing + submission"
  ),
  Deliverable = c(
    "Main codes + paper draft",
    "Results: NOVELIST",
    "Results: POET & PC-adjusted NOVELIST",
    "Results: other estimators",
    "Application completed",
    "Thesis manuscript"
  )
) %>%
  kable(caption = "Project Timeline and Key Milestones")
```

# Expected Contributions

>>>>

---
title: "Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators"
format: 
  pdf:
    include-in-header:
      text: |
        <!-- \usepackage{amsmath} -->
        <!-- \usepackage{mathspec} -->
        \usepackage{algorithm}
        \usepackage{algpseudocode}
        \usepackage[colorlinks=true, linkcolor=blue, citecolor=blue, urlcolor=blue]{hyperref}
        \usepackage{array}
    mathspec: true
    number-sections: true
execute:
  cache: true
bibliography: D:/Github/Recon_Honours_Thesis/references.bib
# bibliographystyle: apa
csl: D:/Github/Recon_Honours_Thesis/apa.csl
---

@@

@@

```{r timeline}
#| echo: false
#| message: false
#| warning: false
library(tibble)
library(knitr)
library(kableExtra)

tibble(
  Period = c(
    "March",
    "April", 
    "May", 
    "June",
    "July-August", 
    "September",
    "October"
  ),
  Task = c(
    "Initial setup and understanding the research scope. Preliminary knowledge and Literature review",
    "Implementing the Min Trace approach with the shrinkage and NOVELIST estimator. Implementing rolling-window cross-validation for choosing NOVELIST threshold parameter. Exploring simulation framework.",
    "Executing simulation on different settings, in order to assess the performance and behaviours of NOVELIST under different conditions. Writing research proposal and presenting research project.",
    "Implementing POET and PC-adjusted NOVELIST estimators. Assessing whether prominent principal components structure can be exploited to improve the out-of-sample forecast performance.",
    "Exploring other high-dimensional covariance estimators",
    "Real-world application + evaluation (e.g. company sales data or Australia tourism data)",
    "Final writing + submission"
  ),
  Deliverable = c(
    "Literature review + paper draft",
    "Main codes for estimators + simulation framework + cross-validation",
    "NOVELIST simulation results + research proposal + presentation",
    "POET & PC-adjusted NOVELIST simulation results",
    "Other estimators simulation results",
    "Application",
    "Thesis manuscript"
  )
) %>%
  kable(
    format = "latex",
    booktabs = TRUE,
    longtable = TRUE,
    caption = "Project Timeline and Key Milestones",
    escape = TRUE
  ) %>%
  column_spec(1, width = "1.9cm") %>%
  column_spec(2, width = "8cm") %>%
  column_spec(3, width = "4.8cm") %>%
  kable_styling(latex_options = "hold_position", font_size = 10)
```

<!-- # Expected Contributions -->
